Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-10 paper_comparison/paper_comparison/paper_comparison.Rmd
fill in p-value cp

Visual inference and conventional hypothesis testing are two distinct statistical procedures. As shown in \ref{fig:p-value-comparison}, the visual test almost always gives higher p-values than the conventional test, suggesting that humans have lower confidence and much higher tolerance of the residual departures than the numerical procedure. In fact, only around 58% of the cases, both tests will agree on the rejection decision given 95% confidence level. And in 41% of the cases, visual test does not reject the null hypothesis but conventional test does. This is an indicator of "false alarm"

>>>>

Visual inference and conventional hypothesis testing are two distinct statistical procedures. As shown in \ref{fig:p-value-comparison}, the visual test almost always gives higher p-values than the conventional test, suggesting that humans have lower confidence and much higher tolerance of the residual departures than the numerical procedure. In fact, only around 58% of the cases, both tests will agree on the rejection decision given 95% confidence level. And in 41% of the cases, visual test does not reject the null hypothesis but conventional test does. Although we know that the all the designed lineups contain various degrees of residual departures and the conventional test is telling truth, analysts and general public as the consumers of the output will possibly not believe in or at least not response to the "false alarm" if they can not see the departures directly from the data plot and view it as impactful. The sensitivity of the conventional test may distract and discourage us from finding a good linear approximation to the data we try to model. This also partly explains why abundance of literature suggesting the use of data plot in regression diagnostics.

### 2022-10-10 paper_comparison/paper_comparison/paper_comparison.tex
fill in p-value cp

Visual inference and conventional hypothesis testing are two distinct
statistical procedures. As shown in \ref{fig:p-value-comparison}, the
visual test almost always gives higher p-values than the conventional
test, suggesting that humans have lower confidence and much higher
tolerance of the residual departures than the numerical procedure. In
fact, only around 58\% of the cases, both tests will agree on the
rejection decision given 95\% confidence level. And in 41\% of the
cases, visual test does not reject the null hypothesis but conventional
test does. This is an indicator of ``false alarm''

>>>>

Visual inference and conventional hypothesis testing are two distinct
statistical procedures. As shown in \ref{fig:p-value-comparison}, the
visual test almost always gives higher p-values than the conventional
test, suggesting that humans have lower confidence and much higher
tolerance of the residual departures than the numerical procedure. In
fact, only around 58\% of the cases, both tests will agree on the
rejection decision given 95\% confidence level. And in 41\% of the
cases, visual test does not reject the null hypothesis but conventional
test does. Although we know that the all the designed lineups contain
various degrees of residual departures and the conventional test is
telling truth, analysts and general public as the consumers of the
output will possibly not believe in or at least not response to the
``false alarm'' if they can not see the departures directly from the
data plot and view it as impactful. The sensitivity of the conventional
test may distract and discourage us from finding a good linear
approximation to the data we try to model. This also partly explains why
abundance of literature suggesting the use of data plot in regression
diagnostics.
